\documentclass[a4paper]{article}

% Table of contents depth
\setcounter{tocdepth}{3}

% Section numbering depth (zero for no numbering)
\setcounter{secnumdepth}{0}

% LaTeX package inclusions
\usepackage[english]{babel}

\usepackage{fullpage} % Page width options

\usepackage{hyperref} % Internal and external references
\usepackage{url}      % Unused?
\usepackage{breakurl} % Support for sensible line breaks in URLS

\usepackage{tabulary} % Fun with tables
\usepackage{float}    % Allows for better placement of tables etc
\usepackage{array}    % More options for tables
\usepackage{multirow} % Support for multi row columns in tables

\usepackage{graphicx} % For picture inclusion
\graphicspath{{images/}}

\usepackage[colorinlistoftodos]{todonotes} % For the inclusion of TODOs
\usepackage[toc,page]{appendix} % Generation of bibliography/appendix

% Source code inclusion
\usepackage{listings}
\lstset{
  tabsize=2,
  basicstyle = \ttfamily\small,
  columns=fullflexible
}
% Usage for the above like so:
% \begin{lstlisting}
%   CODE CODE CODE
% \end{lstlisting}

% In-line code styling (same style as listing)
\newcommand{\shell}[1]{\lstinline{#1}}

% Use roman numerals for page numbers in the contents
\pagenumbering{roman}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title{\textbf{WALRUS:}\\
Exercise classification on embedded hardware}
\date{2017}
\author{
Daniel Clay \\
\emph{Supervised by Dr Thomas Heinis} 
}
\maketitle
\pagebreak
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{Abstract: do this last, goes the advice}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgements}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{Acknowledgements: Dr Heinis et al}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Table of Contents on new page
\pagebreak
\tableofcontents
\pagebreak

% Use arabic numerals after contents
\pagenumbering{arabic}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Motivation}%%%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{I have some, probably}

\subsection{Issues}%%%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{What makes this difficult}

\subsection{Contributions}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{As it says on the tin. List all the deliverables}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Background}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Neural Networks}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{What is the current state of research regarding neural networks?, mostly from Interim Report. Also discuss what frameworks are available?}

\subsection{Embedded Systems}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{Current state of embedded systems etc, including performance}

\subsection{Bluetooth / Bluetooth Low Energy (BLE)}%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{Look, it's a thing. Explain why it's useful}

\subsection{Fitness Trackers}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{Current state of fitness trackers available, mostly from Interim Report}

\subsection{Intel Curie}%%%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{Info about the Intel Curie. Note what is currently available, and what could be available soon, mostly from Interim Report}

\subsection{Bodyweight Exercises}%%%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{Discuss these exercises and their form, mostly from Interim Report}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Design \& Specification}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{Overall design. Note different versions, and throughout note differences due to different versions. This is basically a specification}

\subsection{Hardware}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{Overview of hardware used and specifications for alternative}

\subsubsection{Microcontroller}

\todo[inline]{Details of the microcontroller and specification. Also touch on alternatives. Also also pick a consistent name}

\subsubsection{Linux Computer}

\todo[inline]{For training. Details of my machine and specification}

\subsubsection{Android Phone}

\todo[inline]{Details of my phone and specifications needed}

\subsection{Microcontroller Software Architecture}%%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{Software architecture \& UML diagrams etc for microcontroller}

\subsection{Linux Computer Software Architecture}%%%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{Software architecture \& UML diagrams etc for computer}

\subsection{Android Phone Software Architecture}%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{Software architecture \& UML diagrams etc for Android phone}

\subsection{Data Capture \& Format}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{Data capture and *format specification*. Talk about Curie's IMU, and how to turn the stream of inputs into the desired format for the Neural network}

\subsection{Neural Network Architecture}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{Architecture of the various neural networks. Note that the parameters etc will be decided on after experimentation}

\subsection{Training of Neural Network}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{How to train neural network on computer (and to get the network weights etc back onto the Curie}

\subsection{Classification by the Neural Network}%%%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{Spec for how neural network should classify examples, and output data format for display}

\subsection{Connectivity}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{Data exchange protocol specification etc. How do connect between microcontroller and phone???}

\subsection{Data Display}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{What the phone should display in response to different things}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Project Plan and Management}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Timetable}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{Subsubsections.}

\subsection{Version Control}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{Subsubsections.}

\subsection{Methodologies Used}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{Subsubsections. Include this at all?}

\subsection{Languages \& Libraries Used}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{Subsubsections.}

\subsection{Tools Used}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{Subsubsections.}

\todo[inline]{More Subsections? (Hardware?}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Evaluation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Contribution/Deliverable Progress \& Completion}%%%%%%%%%%%%%%

\todo[inline]{Better name? Which deliverables did I actually deliver}

\subsection{Classifier Performance}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{All the normal classification measures. Will probably need numbers for all the versions}

\subsection{Energy Consumption}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{How long did the battery last? Is this practicable for the smaller form factor Curie etc}

\subsection{Stability \& Ease of Use}%%%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{Does it crash? Is it easy to install and use?}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Work}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Conclusion}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{What have *we* learned? What worked and what didn't, etc}

\subsection{Future Work}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{Where can the technology go from here?}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Appendix 1: User Guide}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Installation}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{How to: install all the stuff. Ideally git repo + single script to install dependencies should be enough}

\subsection{Setup}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{How to get ready to classify (inc. training the network to match your movements, probably. If not this section becomes less useful).}

\subsection{Usage}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo[inline]{How to: actually use the thing}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Bibliography
\newpage
\addcontentsline{toc}{section}{Bibliography}

\begin{thebibliography}{9}

%\bibitem{yes}

\end{thebibliography}

\end{document}
